Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-13 parts/sa.tex
typo

\paragraph{Sequential reachability.}
Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
one can use the same approach as for sub-state reachability by introducing
a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
$\reach_n$ with hitters corresponding the successive local states
(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
$\PHfrappes{b_j}{\reach_0}{\reach_1}$).

>>>>

\paragraph{Sequential reachability.}
Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
one can use the same approach as for sub-state reachability by introducing
a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
$\reach_n$ with hitters corresponding the successive local states
(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
$\PHfrappes{b_j}{\reach_1}{\reach_2}$).
